Paraphrasing for Style

### 2012-09-01 paper/paper.tex
added citations

Paraphrases can differ along many dimensions, including utterance length, diction level, and speech register. 
There is a significant literature in sentence compression aimed at modeling the first of these, length: 
producing meaning-preserving alternations that reduce the length of the input string {\bf TODO:} [citations].
However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?

>>>>

Paraphrases can differ along many dimensions, including utterance length, diction level, and speech register. 
There is a significant literature in sentence compression aimed at modeling the first of these, length: 
producing meaning-preserving alternations that reduce the length of the input string \cite{Chandrasekar96,Vanderwende07,Yatskar10}.
However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?
